---
title: "Result Summary"
ipsum_meta:
  og_url: "https\\://example.com/open/graph/finalURLfor/this"
  og_description: "A modest size description of the content"
  og_image: "https\\://example.com/open/graph/imageURLfor/this"
output: 
  hrbrthemes::ipsum:
    toc: true
---
```{r include=FALSE}
knitr::opts_chunk$set(fig.retina=2)
```

```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
library(hrbrthemes)
library(tidyverse)

source("init.R")
update_geom_font_defaults(font_rc)

h1_null <- readRDS("models/h1_null_min.rds")
h2_null <- readRDS("models/h2_null.rds")
```

## H1.1: Blocked Rules

**(directed)** Higher number of extrapolations for the stimuli of the untrained/incomplete category in the blocked training condition, compared to the mixed training condition, in the transfer phase

### Model Ouput

```{r 1.1-model}
h1_blocked <- readRDS("models/h1_blocked_min.rds")

h1_blocked
```

### Inference / Bayes Factor

```{r 1.1-bf}
bayes_factor(h1_blocked, h1_null)
```


## H1.2: Instructions

**(directed)** Higher number of extrapolations for the stimuli of the untrained/incomplete category in the blocked training condition, compared to the mixed training condition, in the transfer phase

### Model Ouput

```{r 1.2-model}
h1_instructions <- readRDS("models/h1_rules_min.rds")

h1_instructions
```

### Inference / Bayes Factor

```{r 1.2-bf}
bayes_factor(h1_instructions, h1_null)
```


## H1.3: Interaction of Blocked Rules and Instructions

**(undirected, _exploratory_)** Interaction of rule order and the rule instructions on the number of extrapolations within the untrained/incomplete category

### Model Ouput

```{r 1.3-model}
h1_both <- readRDS("models/h1_both_min.rds")

h1_both
```

### Inference / Bayes Factor

```{r 1.3-bf}
bayes_factor(h1_both, h1_blocked)
bayes_factor(h1_both, h1_instructions)
bayes_factor(h1_both, h1_null)
```



## H2.1: Rule Instructions

**(directed)** quicker learning of categories with rule instructions than without in the mixed rule condition

### Model Ouput

```{r 2.1-model}
h2_rules <- readRDS("models/h2_rules.rds")

h2_rules
```

### Inference / Bayes Factor

```{r 2.1-bf}
bayes_factor(h2_rules, h2_null)
```


## H2.2: Interaction of Training Block and Rule Instructions

**(undirected, _exploratory_)** Interaction of learning accuracy between training blocks (3-12) and rule instructions in the blocked rule condition

### Model Ouput

```{r 2.2-model}
h2_interaction <- readRDS("models/h2_inter.rds")

h2_interaction
```

### Inference / Bayes Factor

```{r 2.2-bf}
bayes_factor(h2_interaction, h2_rules)
bayes_factor(h2_interaction, h2_null)
```
