---
title: "INSERT_TITLE_HERE"
ipsum_meta:
  twitter_card: "Summary info for the Twitter Card"
  twitter_site: "\\@sitehandle"
  twitter_creator: "\\@creatorhandle"
  og_url: "https\\://example.com/open/graph/finalURLfor/this"
  og_description: "A modest size description of the content"
  og_image: "https\\://example.com/open/graph/imageURLfor/this"
output: 
  hrbrthemes::ipsum:
    toc: true
---
```{r include=FALSE}
knitr::opts_chunk$set(fig.retina=2)
```

```{r ipsum_setup, message=FALSE, warning=FALSE, cache=FALSE, echo=FALSE}
source("init.R")

# update_geom_font_defaults(font_rc)
```


## look at the data

Aggregate for use in bonimial regression.

```{r 1st}
critems <- simg %>% 
  filter(img_cluster == "untrained") %>% 
  group_by(condition, subj) %>% 
  summarise(
    k = sum(response),
    n = n(),
    p = k / n
  ) %>% ungroup()

glimpse(critems)
```

### refactor to 2x2 design

```{r 2nd}
intact <- critems %>% 
  mutate(
    rrl  = ifelse(condition == "B" | condition == "D", 1, 0),
    srf  = ifelse(condition == "C" | condition == "D", 1, 0)
  )

glimpse(intact)
table(intact$rrl, intact$srf, dnn = c("rrl", "srf"))
```

## model some models to model the modeling

**DISCLAIMER:** no random effects at this point, since this is just about model comparison for now; also iterations, warmups, etc are way too low

### Priors 1st

```{r 3rd}
priors <- c(
  # since ~0.32 is the se, and log(.3) is ~(-1.2)
  set_prior("normal(-1.2, 0.32)", class = "Intercept"), 
  # just following Gelmans recommendations
  set_prior("normal(0, 0.5)", class = "b")
)

priors
```

alternatively: `b = student_t(5, 0, se)` and `Intercept = student_t(5, -1.2, se)`

### m1: Intercept only

**DISCLAIMER:** no priors

```{r 4th}
m_int <- brm(data = intact,
            k|trials(n) ~ 1,
            family = binomial(),
            cores = ncore, iter = 5000, warmup = 1000,
            control = list(adapt_delta = 0.8),
            save_pars = save_pars(all = TRUE)
)

summary(m_int)
```

### m2: full model (...I guess?)

```{r 5th}
m_full <- brm(data = intact,
            k|trials(n) ~ rrl * srf,
            family = binomial(), prior = priors,
            cores = ncore, iter = 5000, warmup = 1000,
            control = list(adapt_delta = 0.8),
            save_pars = save_pars(all = TRUE)
)
```

### m3: rrl only 

```{r 6th}
m_rrl <- brm(data = intact,
            k|trials(n) ~ rrl,
            family = binomial(), prior = priors,
            cores = ncore, iter = 5000, warmup = 1000,
            control = list(adapt_delta = 0.8),
            save_pars = save_pars(all = TRUE)
)
```

### m4: srf only

```{r 7th}
m_srf <- brm(data = intact,
            k|trials(n) ~ srf,
            family = binomial(), prior = priors,
            cores = ncore, iter = 5000, warmup = 1000,
            control = list(adapt_delta = 0.8),
            save_pars = save_pars(all = TRUE)
)
```

## comparison

### ...to intercept only

**rrl > int?**

```{r comp1}
bayes_factor(m_rrl, m_int)
```


**srf > int?**

```{r comp2}
bayes_factor(m_srf, m_int)
```


**full > int?**

```{r comp3}
bayes_factor(m_full, m_int)
```



### to each other?

**rrl <-> srf?**

```{r comp4}
bayes_factor(m_rrl, m_srf)
```

**full > rrl?**

```{r comp5}
bayes_factor(m_full, m_rrl)
```

**full > srf?**

```{r comp6}
bayes_factor(m_full, m_srf)
```

```{r bib, include=FALSE}
# KEEP THIS AT THE END OF THE DOCUMENT TO GENERATE A LOCAL bib FILE FOR PKGS USED
knitr::write_bib(sub("^package:", "", grep("package", search(), value=TRUE)), file='skeleton.bib')
```